A sheaf--function dictionary for algebraic tori over non-archimedean local fields

### 2013-08-16 shanghai.tex
Improved the proof of the lemma on boxtimes in the section pull-backs and products.

\begin{proposition}\label{prop:product}
The rule $\boxtimes : (\cs{L}_1,\cs{L}_2)\to \cs{L}_1\boxtimes\cs{L}_2$ defines an equivalence of categories 
\[
\QC(G_1)\times(G_2) \to \QC(G_1\times G_2)
\]
and 
\[
\begin{tikzcd}[column sep=60]
\arrow{d}{\trFrob{G_1} \times \trFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{\trFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
(G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
\end{tikzcd}
\]
commutes.
\end{proposition}

\begin{proof}
The only non-trivial part is essential surjectivity. Set $G \ceq G_1\times G_1$. Let $\cs{L}$ be a quasicharacter sheaf on $G$. Define $f : G\to G\times G$ by $f(g_1,g_2) = (g_1,e_2,e_1,g_2)$. Observe that $m\circ f = \id_G$. 
Then the isomorphism $\mu : m^* \gcs{L} \to \gcs{L}\boxtimes \gcs{L}$ gives an isomorphism
\[
f^*\mu : f^* m^* \gcs{L} \to f^*(\gcs{L}\boxtimes \gcs{L}) = f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L}.
\]
Observe that $p_1\circ f = r_1 \circ q_1$ and $f_2 = r_2\circ f$ where $p_1 , p_2 : G\times G \to G$ are the usual things and $r_1 : G_1\times G_2 \to G_1$ and $r_2 : G_1\times G_2 \to G_2$ are the obvious things and $q_1 : G_1\to G_1\times G_2$ and  $q_2 : G_2\to G_1\times G_2$ are the usual things. Then $f^*p_1^*\gcs{L} = r_1^* q_1^* \gcs{L}$ and $f^*p_2^*\gcs{L} = r_2^* q_2^* \gcs{L}$. Now $\cs{L}_1 \ceq r_1^* \cs{L}$ is a quasicharacter sheaf on $G_1$ and $\cs{L}_2 \ceq r_2^* \cs{L}$ is a quasicharacter sheaf on $G_2$, by Proposition~\ref{prop:pullback}. Then
$ f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L} = r_1^*\gcs{L}_1\otimes r_2^* \gcs{L}_2 = \gcs{L}_1\boxtimes \gcs{L}_2$. In this way, $\mu$ determines an isomorphism
\[
f^*\mu : \gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2.
\]
So $\boxtimes$ is essentially surjective.
\end{proof}

>>>>

\begin{proposition}\label{prop:product}
The rule $\boxtimes : (\cs{L}_1,\cs{L}_2)\to \cs{L}_1\boxtimes\cs{L}_2$ defines an equivalence of categories 
\[
\QC(G_1)\times (G_2) \to \QC(G_1\times G_2)
\]
(categorical product on the left, product of group schemes over $\Fq$ on the right) and 
\[
\begin{tikzcd}[column sep=60]
\arrow{d}{\trFrob{G_1} \times \trFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{\trFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
(G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
\end{tikzcd}
\]
commutes.
\end{proposition}

\begin{proof}
The only non-trivial part is essential surjectivity. Set $G \ceq G_1\times G_2$. Let $\cs{L}$ be a quasicharacter sheaf on $G$. Define $f : G\to G\times G$ by $f(g_1,g_2) = (g_1,e_2,e_1,g_2)$. Observe that $m\circ f = \id_G$. 
Let $p_1$, $p_2$ be the projection morphisms pictured below:
\[
\begin{tikzcd}
G & \arrow[swap]{l}{p_1} G\times G \arrow{r}{p_2} & G\\
\end{tikzcd}
\]
Then the isomorphism $\mu : m^* \gcs{L} \to \gcs{L}\boxtimes \gcs{L}$ gives an isomorphism
\[
f^*\mu : f^* m^* \gcs{L} \to f^*(\gcs{L}\boxtimes \gcs{L}) = f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L}.
\]
Let $r_1$ and $r_2$ be the projection morphisms pictured below, with sections $q_1$, $q_2$, also morphisms of group schemes:
\[
\begin{tikzcd}
G_1  \arrow[swap, bend right]{r}{q_1} & \arrow[swap, bend right]{l}{r_1} G_1\times G_2 \arrow[bend left]{r}{r_2} &  \arrow[bend left]{l}{q_2} G_2.\\
\end{tikzcd}
\]
Then $p_1\circ f = r_1 \circ q_1$ and $f_2 = r_2\circ f$, 
so $f^*p_1^*\gcs{L} = r_1^* q_1^* \gcs{L}$ and $f^*p_2^*\gcs{L} = r_2^* q_2^* \gcs{L}$. 
Now $\cs{L}_1 \ceq r_1^* \cs{L}$ is a quasicharacter sheaf on $G_1$ 
and $\cs{L}_2 \ceq r_2^* \cs{L}$ is a quasicharacter sheaf on $G_2$, 
by Proposition~\ref{prop:pullback}. 
Then 
\[
f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L} = r_1^*\gcs{L}_1\otimes r_2^* \gcs{L}_2 = \gcs{L}_1\boxtimes \gcs{L}_2.
\]
In this way, $\mu$ determines an isomorphism
\[
f^*\mu : \gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2.
\]
So $\boxtimes$ is essentially surjective.
\end{proof}
